---
title: "Expressed Variant Reporting Results"
author: "Brandon Michael Blobner, Jenny Leopoldina Smith, and Ahmad Al Khleifat"
date: "`r format(Sys.Date(), tz = 'America/Los_Angeles')`"
output:
  blastula::blastula_email:
    always_allow_html: yes
    section_divs: true
    number_sections: true
    fig_caption: true
    includes:
      before_body: email_header.html
      after_body: email_footer.html
    connect_footer: false
---


```{r setup, include=FALSE, echo=FALSE}
require(knitr)
knitr::opts_knit$set(root.dir = here::here())


knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),
                      tidy=TRUE,
                      fig.align='center',
                      fig.width = 5, fig.height = 7)
```

```{r echo=FALSE, message=FALSE}
library(dplyr)
library(magrittr)
library(tidyr)
library(stringr)

library(here)
library(ggplot2)
library(gridExtra)
library(RColorBrewer)
```


Dear { Patient/Clinician },

We have produced a report of your current genetic report produced by `snpReportR` from {institution}. The following synopsis is provided below and an in-depth description of findings and their potential impact are included in the full HTML report. 

If you encounter questions or concerns, please contact { institution } or { doctorInfo }. 


<br><br><br>

# Summary of Findings 

Here are the most relevant findings in your sequencing results

1. GeneA
2. GeneB
3. GeneC


<br><br><br>

# About snpReportR 

<br><br><br>


```{r eval=FALSE, echo=FALSE}
#cid:foobar #worked on pandoc v2.7.3 not on v2.11.4
#here("logos/snpReporter_logo.png") #works in pandoc render, NOT in email body
htmltools::img(src = here("logos/snpReporter_logo.png"),
               alt = 'logo',
               style = 'float: center;padding-right:10px;height:a125px;width:250px')

```

```{r echo=FALSE, eval=FALSE}
#This give me the base64 encoded image, but it will not render into an image in the sent email...
logo <- htmltools::img(src = knitr::image_uri(here("logos/snpReporter_logo.png")),
               alt = 'logo',
               style = 'float: center;padding-right:10px;height:a125px;width:250px')

# # str(logo)
```

<br><br><br>




