---
title: "Expressed Variant Reporting Results"
author: "Brandon Michael Blobner, Jenny Leopoldina Smith, and Ahmad Al Khleifat"
date: "`r format(Sys.Date(), tz = 'America/Los_Angeles')`"
output:
  blastula::blastula_email:
    always_allow_html: yes
    number_sections: true
    fig_caption: true
    connect_footer: TRUE
    
---


```{r setup, include=FALSE, echo=FALSE}
require(knitr)
knitr::opts_knit$set(root.dir = here::here())


knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),
                      tidy=TRUE,
                      fig.align='center',
                      fig.width = 5, fig.height = 7)

getwd()
```

```{r echo=FALSE, message=FALSE}
library(dplyr)
library(magrittr)
library(tidyr)
library(stringr)

library(here)
library(ggplot2)
library(gridExtra)
library(RColorBrewer)
```


Dear { Patient/Clinician },

We have produced a report of your current genetic report produced by `snpReportR` from {institution}. The following synopsis is provided below and an in-depth description of findings and their potential impact are included in the full HTML report. 

If you encounter questions or concerns, please contact { institution } or { doctorInfo }. 


<br><br><br>

# Summary of Findings 

For CSS Styles:
https://emilyriederer.netlify.app/post/rmarkdown-css-tips/

For LATEX PDF templates
https://www.overleaf.com/latex/templates/tu-dublin-computing-poster-template/mpnrbxzvjgsr 

<br><br><br>

# About snpReportR 

<br><br><br>

```{r}
htmltools::img(src = "cid:foobar", 
               alt = 'logo', 
               style = 'float: center;padding-right:10px;height:a125px;width:250px')
```

<br><br><br>

Add a footer too

<br><br><br>


```{cat, engine.opts=list(file = "footer.html")}
<p>This is a footer</p>
```



